Differential invariant signatures for planar Lie group transformations of images

### 2020-11-17 paper/newpaper.tex
T2 section written

\begin{equation}\label{eq:function}
**write me**
\end{equation}

\subsubsection{Example}
Consider as our image, the function $f(x, y) = 0.5 - 0.2x - 0.3y - 0.05x^2 +
0.03xy + 0.04y^2 + 0.03y^3 +0.001x^3 - 0.0015x^2y + 0.002xy^2 - 0.0005y^3$
defined on $[0, 1]\times[0, 1]$.

@@

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{Figs/function}
  \includegraphics[width=.45\textwidth]{Figs/function_scanlines}
  \caption{The test function used in this document, from
  Eq.~\eqref{eq:function}.}\label{fig:function}
\end{figure}

@@

The most basic transformation group of a image is the translation group $T(2): \phi(\mathbf{x}) = \mathbf{x} + \mathbf{t}$. These could arise from actions such as cropping a photo.

@@

Figure~\ref{fig:T2} shows (a) the original image, (b) the translated image by $x,y$, (c) the signature of one of them, (d) the superimposed pair of signatures. Now explain the missing bits.

>>>>

\begin{equation}\label{eq:function}
f(x, y) = \exp(-2x^2 - 4\sin^2(y + 0.5x^2))
\end{equation}

@@

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{Figs/function}
  \includegraphics[width=.45\textwidth]{Figs/function_scanlines}\\
  \caption{The test function used in this document, from Eq.~\eqref{eq:function}.}\label{fig:function}
\end{figure}

@@

The most basic transformation group of a image is the translation group
$T(2) \colon \mathbb{R}^2 \to \mathbb{R}^2$ with elements of the form
$\varphi(\mathbf{x}) = \mathbf{x} + \mathbf{t}$ for fixed $\mathbf{t}$.
These could arise from actions such as cropping a photo.

@@

Figure~\ref{fig:T2} shows (a) the original image, (b) the translated image
under the transformation $(x,y) \mapsto (x + 0.1, y - 0.2)$, (c) the
signature of one of them, (d) the superimposed pair of signatures. The
yellow lines in (c) correspond to where the yellow grid from (a) has been
mapped to on the signature surface. In (d), notice that as some of the
image has moved out of frame, there are parts of the signature near its
boundary that do not overlap.

\begin{figure}
  \centering
  \begin{tabular}{cc}
  \includegraphics[width=.45\textwidth]{Figs/function_scanlines} &
  \includegraphics[width=.45\textwidth]{Figs/f_transformed_T2} \\
  (a) & (b) \\
  \includegraphics[width=.45\textwidth]{Figs/T2_signature} &
  \includegraphics[width=.45\textwidth]{Figs/T2_match} \\
  (c) & (d)
  \end{tabular}
  \caption{(a), (b) The image before and after the T(2) transformation $(x,
  y) \mapsto (x + 0.1, y - 0.2)$. (c) the signature of the
  image (before translation). (d) the signature after the
  translation superimposed.}\label{fig:T2}
\end{figure}
